% Chapter 9

\chapter{Tests with the Users} % Main chapter title

\label{Chapter9} % For referencing the chapter elsewhere, use \ref{Chapter9} 

In this chapter first of all is exposed how the users are defined and what are their characteristics. Also, here are described the test conducted with them and in which ways they are useful to improve the gAn Web's features.   

\section{User's Profile: why?}

Generically a correct understanding of the user is very important to adapt the features of an application to him; In this case is also more important, because the kind of users to that this application is intended to is quite particular.


\section{User's Profile: classification}

\subsection{Generic Characteristics}
In this part of the document we can try to classify the user:
The estimated number of users of the application is around 15.
All the users of gAn Web works as "Shifters" in the AEgIS experiment: so they work with data acquisition and (simple) data analysis.
Usually the user is quite young: around 30-35 years. This is because the most of the time personnel with a major seniority doesn't work with tasks related to data acquisition. 
Half of them are male, and half female: in this particular case we think that it is not relevant in their interaction with gAn Web.
A considerable amount of the users use eyeglasses, and probably some of them pass too many time in front of a screen, but the kind of interaction designed with gAn is usually fast and isn't a big commitment for human eyes. We tried to avoid too many white backgrounds and the use of dazzling colours, but for the images' background they are considered acceptable to improve contrast and let the image to be more clear.  

\subsection{Education Background}
The cultural and educational level of the user is very high: almost all of them have a Phd, and they do a complex scientific job.

All of them have an extraordinary deep understanding of the particles physics: in particular they understand the technical terminology, the jargon in which the logbooks are written (because all the personnel, in shifts, writes the logbooks) and the names of the sensors (this is quite important, each sensor has a proper name, they are very numerous, and the fact that the users can identify them easily is a big ad advantage). 

Other important information: almost every time a user use gAn he is quite sure about what he is looking for. Situation in which the user searches a run number and reads generically the output of an analysis (or thinks about which is the correct analysis to use) is not common: in the most of the use cases the user is pretty sure about what is the information to search and what is the correct analysis. 

A different approach exists for the run number, in this case we must identify two different situation:

\begin{enumerate}

\item The most of the times (around 2/3) the user works with the last run, or the one immediately before. In this case is quite simple identify the correct run.
\item Sometimes the user searches information regarding a past run, that he remember to be interesting for some reason. In this case often the user remembers the date (the precise day, or the week) of the interesting run, but not the run number exactly.

\end{enumerate}

Most of the users are used to use the Linux's terminal, so they are used to quite complex but efficient interaction. A good advantage is that the users are very used to approach new applications, even complex ones, and they learn very rapidly: the advantage is that they are used to give developers hints about what they expect from an new application, because they do it quite often. Actually, the users, in particular the pilot users, are almost co-developers. GAn Web offers them a way to interact efficient like the terminal but easier (hopefully). They also are used to have a feedback for every action they do (using the Linux's terminal you can always know if the program is running, if it is crashed, and what are its outputs).

One of the users if a web developer, so his hints are particularly interesting because is quite expert in the creation of interfaces.
 
All the users have an excellent proficiency in English (they are used to speak English in their work environment). 

\subsection{User's psychological characteristics }
The style of reasoning is quite deductive: the users seem to act in a very scientific way: they observe the situation, they make hypothesis and they experiment them to check if they are true. From the test highlights that the users think mostly in an analytic way, using only seldom their intuition. In gAn Web we can observe that when they are for the first time in front of the application they observe the screen, reading all the tooltips, they understand (of better, they make hypothesis about) what each function do, and they test the functionalities making comments regarding if the application's behavior is the expected one. According the users  propensity the designer of gAn Web tries to let the application acts like the user expects.   

Generically the users work in a quite enthusiast and positive way: the analysis done previous with the Linux terminal was quite time-consuming, so gAn Web is considered as an improvement (or at least, a step in the right direction) and the users seems to be quite happy to use it. All the people showed in the tests the maximum possible commitment and professionalism (in this way the opportunity to test the application directly with real users was very helpful).

Is possible to analyse the arousal of the users with from the point of view of the Yerkes–Dodson's Law: the situation seems to be favorable: nobody of the user 
has problems with low arousal or too much performance anxiety (probably no one seemed himself under the judgement), so the personal activation of the users seems to be optimal.

\subsection{User's level of expertise }
At this stage all the users are beginners, but generically the application is simple and, except that the first moment for understanding the basic functionalities they can reach a good level of expertise. A big advantage is that almost all the users understand what the application does, which are the mathematical principles on which gAn is based, and how this application is integrated in their tasks.   
All the users are absolutely expert pc-users.
The two pilot-users can play the role of super-users, able to be an interface between the design of the application's interface and the needs of the users. They are also the developer of the pre-existent application, on which the interface is based. So they can be an extremely useful resource.  

\subsection{Environment }
The environment is a normal office. Often the users work in night shifts, and the only possible negative effect of the environment is the tiredness of the users, able to damage their arousal. 

\section{How the tests take place} 
%TODO %TODO %TODO %TODO %TODO %TODO %TODO %TODO 
% according THE STAGES BEFORE THERE IS A TEST WITH PILOTS: EVENTUALLY PUT THEM in chapter before
% carousel is useless... 
% multiple stages are not priority
% images with more information!!
% select gan is useless
% select root is useless


This test is divided in three parts: 
\begin{enumerate}
\item
The first is an observation of the behavior of the user with the application: the developer tells to the user only a few information: the fact that this application can transform a run number and a kind of analysis. 
The first idea was follow a pattern in which the developer asks to the user to use this application during the shift, in the situation that he considers it useful: in this situation the user talks about what he is doing, and makes comments, and the developer observe and take notes about what happens (and this pattern was effectively applied with 1/3 of the users), but to test the biggest possible numbers of users and recover more information, in 2/3 of the cases the developer ask to the user to try to use the application in a test situation (not a really work situation) and to reason about what he is doing.
\item
The second consists in the proposition of a standard survey about the application to the user, to be compiled. This survey is the standard SUS survey. This choice is related to the fact that using a standard survey we can have an high quality already testes survey with precise and organized closed questions, able to give us an idea about the overall result of the interface. 
\item 
The third part consists in a brief discussion with the user: the designer asks him in which way this application can be more useful and if there are in his opinion some good ideas to implement able to improve the helpfulness of the application.

\end{enumerate} 

\subsection{Preliminary observations}
It is interesting to observe that it is very important to encourage the users to criticise the application: if fact the developer and the users work together for some weeks, and it is possible that the users are too gentle in the judging of the application, because they don't want to be offensive. Instead, is necessary say them that all their critics are absolutely useful to improve the result, because the developer cannot understand alone what can be modified. 
There is an advantage: one of the users is a web developer, so he is very expert not only in the domain of the physics but also in the design of web interfaces: the final discussion with him is a source of ideas.  

\subsection{Execution and Results}
The first part of the test, the one related to the observation of the users working with the application and talking about what they do, gived a big amount of useful information and let the developer observe a good amount of problems and errors. 
The biggest part of the problem is founded by observing the behaviors of the user and asking directly to him if there is a problem: for example, if the user search for a while how he can enable a sensor and has some difficult to understand how to do it, the developer can listen his comments, understanding his reasons about where he thinks this option can be, shows him where actually the sensor is, and understand that probably the location of the sensor option is not clear. 
Here is a list of problems found in this phase:

\begin{enumerate}

\item
Almost all the users tried very often to change a particular parameter by the configuration page, named "scint rebin", related to the thickness of the points that are fitted to create a function. Moving this parameter the user can modify a particular type of analysis named "TMeas", according to different exigences. Before the test was not so evident that this parameter was so important, and actually in the second version it is not in the list of parameters that the web interface can modify. So in the tests the most of the user manually changed it by a text editor in the configuration file on the server: surely it is unacceptable and this problem must be solved to allow the application work in this particular situation.

\item 
The main options in the configuration page are related to the activation or de-activation of sensors, but the users actually don't use them very often, because  the default values are acceptably correct. So a good idea is to highlight other setting options, and move the rarely used ones in other part of the screen.

\item
In the page that shows the images the user can by a selector choose if he wants want to see the images in a big, a middle, or a little format. During the test no one used this opportunity, and when the developer asked to the users if this control can be useful they simply say that the correct dimension of the image the "big" solution, with the image that cover (almost) all the screen in width. In this case the user can easily read all the information in the image. At this point is possible to observe that the "image dimension control" is useless, and it is a good idea remove it (or at least move it in another part of the screen)   

\item
The interaction of the users with the personal output is particular: during the test the users read it rapidly, but actually they take from there only few information contained in 2-3 rows. Actually in each type of analysis in the eighty percent of the situation there are a few important information, and only in the other cases the user must read all the rest of the output (but in probably 20 percent of the cases he must). So a good idea is to highlight the more important parts (that varies based on the type of the analysis), to organize in groups the "sometimes important" parts, and to hide all the others (there are some rows that are actually important only in the debug phase, that the user never does.. so we can improve the clearness hiding them).

\item 
One of the worst problems is the maybe half of the users don't understand that if they click on the image they can access a lot of information such as other representation, drawing options, opportunity to zoom in or out, labels. In that cases almost all the users asked directly to the developer how to act this commands, because they are absolutely necessary to the correct use of the application. This control is probably the biggest improvement between gAn and gAn Web, because give to the users new opportunity of understanding what is happening in the experiment through information related to the images (the previous version, before gAn, had only png-format images, without this controls), so the fact that the users often don't find it is a big deal. A solution can be create a label-advice to give the user a clearer vision.

\item
Some users, when is in the textual-output page, have some difficulties in finding the command to move to the images pages: probably the button is not sufficiently evident in the screen. This problem can be an impediment with new users so the best idea is solve it, re-thinking the distribution of the buttons in this page, that are actually not very clear. 

\end{enumerate}

The second part, the one related with the surveys, was actually a bit less useful, because the results seemed to be too high if compared with the amount of problems founded in the first test (probably the users simply tried to be gentle with the developer).

The third part, the one that consists in the discussion with the user, was very helpful: almost all the user proposed new ideas (all of them are useful, the most of them are effectively implementable), and new functionalities. Some of the functionalities was asked by almost all the users, so they probably are absolutely important to improve the interaction quality. 

Here is a list of observations obtained in the third phase, through discussions with the users:

\begin{enumerate}

\item 
Probably inserting a tooltip on each button the overall clearness of the product can grow, but it is important to be careful with the risk of covering with the tooltips other buttons. For some commands the tooltips must be more long and precise, because they are not so easy to understand (the pilot users can understand them better because they are very expert in the domain, but it is not always clear for everybody).  

\item
Actually the names of some buttons are not clear. At this stage the developer is not a deep expert of the domain, but probably is more expert than at the beginning, so a general re-discussion of all the names of the buttons (and related tooltips) seems to be a good idea.

\item 
The application is though to be used in the standard AEgIS' experiment screens, that are quite large. But sometimes the users use it from home, and the application must be adaptive to smaller screens (there are some little problems, such as buttons overlapping).

\item
A complex topic: probably can be useful a relation between the run numbers and the logbook of the AEgIS experiment, to allow the user to easily understand on which run he prefers to work with.

\end{enumerate}

\subsection{Is the testing finished here?}

No it is not. The application is entering right in this moment in the standard working processes of the AEgIS experiment. The web application can be prepared to meet the exigences that exist right now, but according to the dynamism of the experimental environment is highly probable that the continuous changing of the back-end (gAn) will lead to a need of constant upgrade of the requirements. In this situation the users will continue to utilise the application, to find new problems, and this fact will route the developer to a continuous process of adaptation.   